---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aranet4r

<!-- badges: start -->
<!-- badges: end -->

The [Aranet4](https://aranet.com/products/aranet4/) is a portable indoor air quality sensor for measuring CO^2^, temperature, atmospheric pressure and relative humidity. These devices are accurate and fun to use, however they are unable to store historic measurements for longer than a fortnight. This package is designed to combine exported Aranet files (in CSV format) into a single dataframe.  

Currently, this package has a single function which combines all your Aranet files into one and removes duplicate entries. Eventually this package will include functions to plot these results, add them to a database, and potentially connect directly to one's device.

## Installation

You can install the development version of aranet4r from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("samherniman/aranet4r")
```

## Reccommended workflow

The following is the workflow that I use, feel free to use whatever method you would like.

1. Connect to your Aranet4 through Bluetooth on your phone 📱 using the Aranet4 app (available on the App Store and Google Play Store)
2. Export Aranet data to a cloud drive that syncs with your computer, like iCloud. Share menu >> save to files >> new folder (name it _Aranet4_ or something) >> save
3. Use `read_aranet("path/to/your/aranet/files")` to read in the files

```{r example}
library(aranet4r)

df <- read_aranet(system.file("extdata", package = "aranet4r"))
```

```{r df}
df
```

